---
title: "reproducable pitch"
author: "Nishitha Chowdary"
date: "26/07/2020"
output:
  slidy_presentation: default
  ioslides_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Shiny Application

#### To analyze the code you can go to https://github.com/NVS143/shiny/tree/master/newapp
#### To see the shiny app you can go to https://bidalika-20.shinyapps.io/newapp/

## What is the function of this application ?

This application is ment to help you in 
visualisation of the ploing of the random data.

- It allows you to visualise the ploting of random 
number of points within a specified x and y range .
- You can use the slider to select the value of minimum 
and maximum of X Axis and Y Axis.
- And then you can check the check boxes according 
to your wish if you want to see or hide the x label 
or y label or the main title of the graph.

## R Output
The R code that is necessary before running any shiny application.
```{r echo=TRUE}
library(shiny)
```